---
title: "analyzeAll"
author: "Alex Holcombe"
date: "2/26/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

Exclude trials where target was not presented.

Exclude other cases where SPE not applicable, namely Response.pos == FALSE

* Response.Pos == False indicates either		
  + the participant reported "0"
  + there was no target on that trial
  + the participant reported a stimulus that was not presented

```{r load_and_preprocess, echo=FALSE}

fileWithPath<- file.path("dataRaw",'allDaysData.RData') 
if (file.exists( fileWithPath )) {
  load ( fileWithPath, verbose=TRUE  ) #loads allDays
}

library(dplyr)
#Exclude trials where target was not presented
allDays <- allDays %>% filter(targetSP != 0)
#Exclude other cases where SPE not applicable
#Response.Pos == False indicates either		a) the participant reported "0"
# b) there was no target on that trial
# c) the participant reported a stimulus that was not presented
allDays <- allDays %>% filter(Response.Pos != FALSE)
```


Install the mixture modeling R library
```{r install}
#devtools::install_github('alexholcombe/mixRSVP',build_vignettes=TRUE)  #If want latest version
library(mixRSVP)

```

Set up the experiment-specific parameters 

```{r detailsNeededForMixtureModeling}

numItemsInStream<- 16 #from their Methods section  
annotateIt<-TRUE
minSPE<- -13 #targetSP = 14, subject reports first letter in stream (1)
maxSPE<- 13 #targetSP = 3 and response position is 16```
```

Ultimately want to analyze data broken down by:
* Group (determines in which serial positions the targets appeared)
* Condition (3-day, 2-day, 1-day)
* targetSP  (formerly known as TargPos (target position this trial))
* Epoch (groups of 3 blocks)
* Subject

```{r factors to break down data by}

condtnVariableNames <- c("Group","Condition","targetSP", "Block","Subject")  
```


```{r analyze, echo=FALSE}

debugging<- TRUE
if (debugging) {
  #take a subset of the data just during debugging because analysis takes all night maybe
  df<- allDays %>% filter(Group==1,Block<8,Condition=="one_day", Subject<17)
}
  
estimates<- df %>%  
    group_by_(.dots = condtnVariableNames) %>%  #.dots needed when you have a variable containing multiple factor names
    do(  analyzeOneConditionDF(.,numItemsInStream,parameterBounds(), nReplicates=3)  )

head(estimates)

```
Parameter estimates done.

```{r saveParameterEstimates, echo=FALSE}

estimates<- estimates %>% mutate(mixModelFitsBetter = (pLRtest<.05))
  
destination<- file.path("results","estimates.csv")

#Convert tibble to dataframe so can be written to csv
estimatesDf <- data.frame(estimates)
write.csv(estimatesDf, destination)

```
Estimates saved to file.
