---
title: "inspect histograms"
author: "Alex Holcombe"
date: "2/26/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

Exclude trials where target was not presented.

Exclude other cases where SPE not applicable, namely Response.pos == FALSE

* Response.Pos == False indicates either		
  + the participant reported "0"
  + there was no target on that trial
  + the participant reported a stimulus that was not presented

```{r load_and_preprocess, echo=FALSE}

fileWithPath<- file.path("dataRaw",'allDaysData.RData') 
if (file.exists( fileWithPath )) {
  load ( fileWithPath, verbose=TRUE  ) #loads allDays
}

library(dplyr)
#Exclude trials where target was not presented
allDays <- allDays %>% filter(targetSP != 0)
#Exclude other cases where SPE not applicable
#Response.Pos == False indicates either		a) the participant reported "0"
# b) there was no target on that trial
# c) the participant reported a stimulus that was not presented
allDays <- allDays %>% filter(Response.Pos != FALSE)
```


Install the mixture modeling R library
```{r install}
#devtools::install_github('alexholcombe/mixRSVP',build_vignettes=TRUE)  #If want latest version
library(mixRSVP)

```

Set up the experiment-specific parameters 

```{r detailsNeededForMixtureModeling}

numItemsInStream<- 16 #from their Methods section  
annotateIt<-TRUE
minSPE<- -13 #targetSP = 14, subject reports first letter in stream (1)
maxSPE<- 13 #targetSP = 3 and response position is 16```
```

Ultimately want to analyze data broken down by:
* Group (determines in which serial positions the targets appeared)
* Condition (3-day, 2-day, 1-day)
* targetSP  (formerly known as TargPos (target position this trial))
* Block (epochs of trials basically)
* Subject


```{r plot one graph}

dg <- allDays %>% filter(Group==1, Condition=="one_day", Block==2, Subject==12)

plotContinuousGaussian<-TRUE
g<- plot_hist_with_fit(dg,minSPE,maxSPE,df$targetSP,numItemsInStream,plotContinuousGaussian,annotateIt, FALSE)
library(ggplot2)
g<-g + annotate("text", x = 12, y = 25, label = "Group 1, one_day, Block 2, Subject 12")
show(g)

```

Define function to plot bunch of subjects.

Facets by "Subject+targetSP~Block", meaning that should break the data down by Group and Condition separately.


```{r, echo=TRUE, message=TRUE}

library(ggplot2)

plotBunch<- function(df,curves) {
  #Columns are epochs
  #Label rows by Subject+targetSP combinations. Outermost label is Subject, inner is targetSP
  g=ggplot(df, aes(x=SPE)) + facet_grid(Subject+targetSP~Epoch) #,  scales="free_y")
  g<-g+geom_histogram(binwidth=1,color="grey90") + xlim(minSPE,maxSPE)
  g<-g+ geom_text(x=12, y= 33, aes(label = Subject)) #inset subject name/number. Unfortunately it overwrites itself a million times
  g<-g +theme_apa() #+theme(panel.grid.minor=element_blank(),panel.grid.major=element_blank())# hide all gridlines.
  #g<-g+ theme(line=element_blank(), panel.border = element_blank())
  sz=.8
  #Plot the underlying Gaussian , not just the discretized Gaussian. But it's way too tall. I don't know if this is 
  #a scaling problem or what actually is going on.
  #g<-g + geom_line(data=gaussFine,aes(x=x,y=gaussianFreq),color="darkblue",size=1.2)
  
  if (!is.null(curves)) {
    g<-g+ geom_point(data=curves,aes(x=x,y=combinedFitFreq),color="chartreuse3",size=sz*2.5)
    #g<-g+ geom_line(data=curves,aes(x=x,y=guessingFreq),color="yellow",size=sz)
    #Discretized Gaussian
    #g<-g+ geom_line(data=curves,aes(x=x,y=gaussianFreq),color="lightblue",size=sz)
    
    #mixSig - whether mixture model statistically significantly better than guessing
    curves <- dplyr::mutate(curves, mixSig = ifelse(pLRtest <= .05, TRUE, FALSE)) #annotate_fit uses this to color the p-value
    g<- annotate_fit(g,curves) #assumes curvesDf includes efficacy,latency,precision
    #Somehow the which mixSig (TRUE or FALSE) is red and which green is flipped relative to plot_hist_with_fit even though
    #identical commands are used. I haven't been able to work out why.
    #g<- g + scale_color_manual(values=c("red","forestgreen")) #already done in annotate_fit
  }
  return (g)   
}  
```

Epoch (groups of 3 blocks) is the smallest group of trials that Shin & Junker want a graph for.

So, create epochs out of group triplets, specifically
 blocks 2-4, 5-7, [skip 8 because practice], 9-11, 12-14, [skip 15 because practice], 16-18, and 19-21


```{r create Epoch variable}

lookupEpoch= data.frame( 
  Epoch=c("practice1", "1","1","1","2","2","2","practice2","3","3","3","4","4","4", "practice3",  "5","5","5","6","6","6"),
  Block=c(1,           2,3,4,         5,6,7,    8,          9,10,11,   12,13,14,     15,     16,17,18, 19,20,21))

allDays <- plyr::join(allDays,lookupEpoch,by='Block') #https://stackoverflow.com/questions/10158617/how-do-i-replace-numeric-codes-in-a-data-frame-with-value-labels-from-a-data-fr?noredirect=1&lq=1

#Add practice TRUE/FALSE column
allDays$practice <- FALSE
allDays<-allDays %>% mutate(practice= ifelse(Epoch=="practice1" | Epoch=="practice2" | Epoch=="practice3", TRUE, FALSE)) #https://stackoverflow.com/questions/24459752/can-dplyr-package-be-used-for-conditional-mutating#24459900
```

plotBunch works: show graphs without curves.

```{r test plotBunch}

dg <- allDays %>% filter(Group==1, targetSP<=7, Condition=="one_day", Subject==12, practice==FALSE)

plotBunch(dg,NULL) #without curves

```

```{r factors to break down data by}

condtnVariableNames <- c("Group","Condition","targetSP","Subject","Epoch")  
```

Fit the data, add the curves to the graph.

```{r}

curves<- dg %>% group_by_at(.vars = condtnVariableNames) %>% 
  do(calc_curves_dataframe(.,minSPE,maxSPE,numItemsInStream))

```

```{r}
g<-plotBunch(dg,curves)
g
```






Need to avoid the "Column `warnings` can't be converted from character " problem.

```{r}
dg <- allDays %>% filter(Group==1, Condition=="one_day", Epoch==2, Subject==12)

curves<- dg %>% group_by_at(.vars = condtnVariableNames) %>% 
  do(calc_curves_dataframe(.,minSPE,maxSPE,numItemsInStream))

plotBunch(dg,curves)


```

```{r}

dg <- allDays %>% filter(Group==1, Condition=="one_day")
dg <- allDays %>% filter(Group==1, Condition=="one_day", Block==2)

curves<- dg %>% group_by_at(.vars = condtnVariableNames) %>% 
  do(calc_curves_dataframe(.,minSPE,maxSPE,numItemsInStream))
#Fixed warnings binding error
```  

```{r get ready to plot bunches}
dg <- allDays %>% filter(Condition=="one_day", Block==2)
curves<- dg %>% group_by_at(.vars = condtnVariableNames) %>% 
  do(calc_curves_dataframe(.,minSPE,maxSPE,numItemsInStream))
```
  
```{r, fig.height=100, fig.width=10}

#plotBunch will break down the data by Epoch, Subject, TargetSP
#So in calling it, we need to loop over only Group and Condition, plus
#divide the subjects into manageable groups

#A good number of rows for fig of height 100 in html is 32.
#Each subject gets 2 rows. Therefore find the 16-subject intervals
subjectsPerGraph<-6
#length(unique(df$subject[ df$subject < "AQ" ]))
numSs<- length( unique(dg$Subject) )
subjectBreaks<- seq(1,numSs,subjectsPerGraph)

subjCutoffs<- unique(dg$Subject)[subjectBreaks]
#add last subject to cutoff list
subjCutoffs<- c( subjCutoffs, tail(unique(dg$Subject),1) )
#for (i in 1:(length(subjCutoffs)-1)) {
for (i in 1:1) {

  subjMin <- subjCutoffs[i]
  subjMax<- subjCutoffs[i+1]
  dh<- dg %>% filter(Subject >= subjMin, Subject <= subjMax)
  curvesThis <- curves %>% filter(Subject >= subjMin, Subject <= subjMax)
  
  h<-plotBunch(dh,curvesThis)
  print(paste0("Showing another set of Ss,",subjMin," to ",subjMax))
  plotTitle<- paste0('Ss ',subjMin,'->',subjMax)
  plotTitle<- paste0(plotTitle,'.png')
  plotPath<- 'plots'
  #show(h)
  ggsave(file.path(plotPath,plotTitle),bg="transparent",limitsize=FALSE ) #bg option will be passed to png
}

  
```


