---
title: "inspect histograms"
author: "Alex Holcombe"
date: "2/26/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

Exclude trials where target was not presented.

Exclude other cases where SPE not applicable, namely Response.pos == FALSE

* Response.Pos == False indicates either		
  + the participant reported "0"
  + there was no target on that trial
  + the participant reported a stimulus that was not presented

```{r load_and_preprocess, echo=FALSE}

fileWithPath<- file.path("dataRaw",'allDaysData.RData') 
if (file.exists( fileWithPath )) {
  load ( fileWithPath, verbose=TRUE  ) #loads allDays
}

library(dplyr)
#Exclude trials where target was not presented
#Exclude other cases where SPE not applicable
#Response.Pos == False indicates either		a) the participant reported "0"
# b) there was no target on that trial
# c) the participant reported a stimulus that was not presented
allDays <- allDays %>% filter(targetSP != 0) %>% filter(Response.Pos != FALSE)
 
```


Install the mixture modeling R library
```{r install}
#devtools::install_github('alexholcombe/mixRSVP',build_vignettes=TRUE)  #If want latest version
library(mixRSVP)

```

Set up the experiment-specific parameters 

```{r detailsNeededForMixtureModeling}

numItemsInStream<- 16 #from their Methods section  
annotateIt<-TRUE
minSPE<- -13 #targetSP = 14, subject reports first letter in stream (1)
maxSPE<- 13 #targetSP = 3 and response position is 16```
```

Ultimately want to analyze data broken down by:
* Group (determines in which serial positions the targets appeared)
* Condition (3-day, 2-day, 1-day)
* targetSP  (formerly known as TargPos (target position this trial))
* Block (epochs of trials basically)
* Subject

```{r}
condtnVariableNames <- c("Group","Condition","targetSP","Subject","Epoch")  
```

Define function to plot bunch of subjects.

Facets by "Subject+targetSP~Block", meaning that should break the data down by Group and Condition separately.

Epoch (groups of 3 blocks) is the smallest group of trials that Shin & Junker want a graph for.

So, create epochs out of group triplets, specifically
 blocks 2-4, 5-7, [skip 8 because practice], 9-11, 12-14, [skip 15 because practice], 16-18, and 19-21


```{r create Epoch variable}

lookupEpoch= data.frame( 
  Epoch=c("practice1", "1","1","1","2","2","2","practice2","3","3","3","4","4","4", "practice3",  "5","5","5","6","6","6"),
  Block=c(1,           2,3,4,         5,6,7,    8,          9,10,11,   12,13,14,     15,     16,17,18, 19,20,21))

allDays <- plyr::join(allDays,lookupEpoch,by='Block') #https://stackoverflow.com/questions/10158617/how-do-i-replace-numeric-codes-in-a-data-frame-with-value-labels-from-a-data-fr?noredirect=1&lq=1

#Add practice TRUE/FALSE column
allDays$practice <- FALSE
allDays<-allDays %>% mutate(practice= ifelse(Epoch=="practice1" | Epoch=="practice2" | Epoch=="practice3", TRUE, FALSE)) #https://stackoverflow.com/questions/24459752/can-dplyr-package-be-used-for-conditional-mutating#24459900
```


Get ready to plot bunches by fitting data, calculating psychometric curves.   will take up pages and pages of NaN warnings, and takes nearly 12 hours. Then save data so part2 can do the graphs.

```{r get ready to plot bunches, echo=FALSE, message=FALSE}
dg <- allDays # %>% filter(Condition=="one_day", Block==2)
curves<- dg %>% group_by_at(.vars = condtnVariableNames) %>% 
  do(  mixRSVP::calc_curves_dataframe(.,minSPE,maxSPE,numItemsInStream)   )
save(curves,dg,file='results/inspectHists.Rdata')
```

How do I get the estimates out of this? Or was there a way to send calc_curves_dataframe the estimates?
