---
title: "inspect histograms"
author: "Alex Holcombe"
date: "2/26/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load data, specifically curves and dg
```{r}

load('results/inspectHists.Rdata')  #Contains the psychometric curves and was created by inspectHistsPart1.Rmd
library(mixRSVP) #for themeAPA
library(dplyr)
library(ggplot2)
minSPE<- -13 #targetSP = 14, subject reports first letter in stream (1)
maxSPE<- 13 #targetSP = 3 and response position is 16```
source('plotBunch.R')

curves$practice <- FALSE
curves<-curves %>% mutate(practice= ifelse(Epoch=="practice1" | Epoch=="practice2" | Epoch=="practice3", TRUE, FALSE))
```

```{r, fig.height=100, fig.width=10}

#plotBunch will break down the data by Epoch, Subject, TargetSP
#So in calling it, we need to loop over only Group and Condition, plus
#divide the subjects into manageable groups

#A good number of rows for fig of height 100 in html is 32.
#Each subject gets up to 12 rows, depending on how many target positions they did. Therefore find the 8-subject intervals
subjectsPerGraph<-2
#length(unique(df$subject[ df$subject < "AQ" ]))
numSs<- length( unique(dg$Subject) )
subjectBreaks<- seq(1,numSs,subjectsPerGraph)

subjCutoffs<- unique(dg$Subject)[subjectBreaks]
#add last subject to cutoff list
subjCutoffs<- c( subjCutoffs, tail(unique(dg$Subject),1) )
for (i in 1:(length(subjCutoffs)-1)) {
  subjMin <- subjCutoffs[i]
  subjMax<- subjCutoffs[i+1]
  dh<- dg %>% filter(practice==FALSE) #Otherwise graph has too many columns to see the data
  dh<- dh %>% filter(Subject >= subjMin, Subject <= subjMax)
  curvesThis <- curves %>% filter(Subject >= subjMin, Subject <= subjMax, practice==FALSE)
  print(paste0("Trying to plot another set of Ss,",subjMin," to ",subjMax))
  h<-plotBunch(dh,curvesThis,minSPE,maxSPE)
  show(h)
  plotTitle<- paste0('Ss ',subjMin,'->',subjMax)
  plotTitle<- paste0(plotTitle,'.png')
  plotPath<- 'plots'
  ggsave(file.path(plotPath,plotTitle),bg="transparent",width=10,height=30,limitsize=FALSE ) #bg option will be passed to png
}
  
```


