---
title: "investigate wierd ones"
author: "Alex Holcombe"
date: "2/8/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load some data. Group 3 means all serial positions were used.

```{r load_and_clean}
estimates<-read.csv( file.path("results",'estimates.csv') )
library(ggplot2)
library(dplyr)

```

Install the mixture modeling R library
```{r install}
#devtools::install_github('alexholcombe/mixRSVP',build_vignettes=TRUE)  #If want latest version
library(mixRSVP)

```

Set up the experiment-specific parameters 

```{r detailsNeededForMixtureModeling}

minSPE<- -13 #targetSP = 14, subject reports first letter in stream (1)
maxSPE<- 13 #targetSP = 3 and response position is 16```
numItemsInStream<- 16 #from their Methods section  

```

WHERE DOES DATA COME FROM? IS IT THE SAME AS alldays?
```{r}
fileWithPath<- file.path("dataRaw",'allDaysData.RData') 
if (file.exists( fileWithPath )) {
  load ( fileWithPath, verbose=TRUE  ) #loads allDays
}
#Exclude cases where SPE not applicable
# When targetSP==0, that is a catch trial, no target presented
#Response.Pos == False indicates either		a) the participant reported "0"
# b) there was no target on that trial (also indicated by targetSP==0?)
# c) the participant reported a stimulus that was not presented
data <- allDays %>% filter(targetSP != 0) %>% filter(Response.Pos != FALSE)

```
Inspect 914. This subject is ok.
```{r plot914, echo=FALSE, message=FALSE, fig.cap = "Fitted guessing distribution in yellow, discretized Gaussian in light blue, combined in green, dark blue is continuous Gaussian"}

d914<- dplyr::filter(data,Subject==914)  
plotContinuousGaussian<- TRUE 
annotateIt<-TRUE
g<- plot_hist_with_fit(d914,minSPE,maxSPE,d915$targetSP,numItemsInStream,
                        plotContinuousGaussian,annotateIt, FALSE)
g <- g + geom_vline(xintercept=0)

g + annotate("text", x = 12, y = 25, label = "914")
```

Inspect strange case of subject #915. Turns out it's actually fine, it's just that they didn't report seeing a letter very often, so it doesn't show up on the graph with common scale at bottom."

```{r plot915, echo=FALSE, message=FALSE, fig.cap = "Fitted guessing distribution in yellow, discretized Gaussian in light blue, combined in green, dark blue is continuous Gaussian"}

d915<- dplyr::filter(data,Subject==915)  
plotContinuousGaussian<- TRUE 
annotateIt<-TRUE
g<- plot_hist_with_fit(d915,minSPE,maxSPE,d915$targetSP,numItemsInStream,
                        plotContinuousGaussian,annotateIt, FALSE)
g <- g + geom_vline(xintercept = 0)
g + annotate("text", x = 12, y = 25, label = "915")

```

Also use plotBunch from plotBunch.r, which uses  facet_grid(Subject+targetSP~Epoch)

```{r}
lookupEpoch= data.frame( 
  Epoch=c("practice1", "1","1","1","1","1","1","practice2","2","2","2","2","2","2", "practice3",  "3","3","3",  "4","4","4"),
  Block=c(1,              2,3,4,5,6,7,             8,          9,10,11,12,13,14,        15,     16,17,18,    19,20,21))

data <- plyr::join(data,lookupEpoch,by='Block') #https://stackoverflow.com/questions/10158617/how-do-i-replace-numeric-codes-in-a-data-frame-with-value-labels-from-a-data-fr?noredirect=1&lq=1
dh <- data %>% dplyr::filter(Subject>=914)
source('plotBunch.R')
h<-plotBunch(dh,NULL,minSPE,maxSPE)
h
```