---
title: "investigate wierd ones"
author: "Alex Holcombe"
date: "2/8/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load some data. Group 3 means all serial positions were used.

```{r load_and_clean}
estimates<-read.csv( file.path("results",'estimates.csv') )
library(dplyr)

```

Install the mixture modeling R library
```{r install}
#devtools::install_github('alexholcombe/mixRSVP',build_vignettes=TRUE)  #If want latest version
library(mixRSVP)

```

Set up the experiment-specific parameters 

```{r detailsNeededForMixtureModeling}

annotateIt<-TRUE
minSPE<- -13 #targetSP = 14, subject reports first letter in stream (1)
maxSPE<- 13 #targetSP = 3 and response position is 16```
```

Inspect strange case of subject #915. Turns out it's actually fine, it's just that they didn't report seeing a letter very often, so it doesn't show up on the graph with common scale at bottom.

```{r plot915, echo=FALSE, message=FALSE, fig.cap = "Fitted guessing distribution in yellow, discretized Gaussian in light blue, combined in green, dark blue is continuous Gaussian"}

d915<- dplyr::filter(data,Subject==915)  
plotContinuousGaussian<-TRUE; annotateIt<-TRUE
g<- plot_hist_with_fit(d915,minSPE,maxSPE,d915$targetSP,numItemsInStream,plotContinuousGaussian,annotateIt, FALSE)
g + annotate("text", x = 12, y = 25, label = "915")
```
