---
title: "Overview"
author: "Alex Holcombe"
date: "2/21/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

There are both "training" blocks, "practice" blocks (1,8,15, which I think were the first block of each day?), and "transfer" blocks (vary with day condition).


Targets were in serial positions 3-14 for Group 3 in the training sessions.  Blocks 2-4 correspond to training for the 1-Day condition, 2-7 and 9-11 for the 2-Day condition, and blocks 2-7, 9-14, and 16-18 for the 3-Day condition (blocks 1, 8, and 15 were "practice blocks" of 10 or so trials).  So, Group 3 of the 3-Day condition would have the most data if you want target positions to be randomized.


We would also want to have the parameters for transfer for each target position (4, 7, 10, 13) separately from the training phase. This would be for the 1-, 2-, and 3-day conditions.

Finally, we would like to have parameters for the last epoch of training for each subject in the 1-, 2-, and 3-day conditions. An epoch is defined as 3 blocks.

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
